---
title: "Seurat testing"
output: html_notebook
---


#Necessary libraries
```{r, echo = FALSE} 
source("http://bioconductor.org/biocLite.R")
library(Seurat)
library(tidyverse)
```

#Load Meta data as provided from authors
```{r}
sample_sheet = read.table("cerebellum_cell_metadata.tsv", sep = "\t", header = TRUE)
```


# What cell types were detected?
# Which timepoints have purkinje cells and how many?
```{r}
levels(sample_sheet$cell_type)
sample_sheet %>% filter(cell_type=="Purkinje") %>%
  group_by(sample_id) %>%
  count()
```
# test analysis of timepoint E14A
# read data, create seurat subject, add timepoint specific meta data
```{r}
e14a_data = Read10X("~/Documents/data/E14A/")
e14a = CreateSeuratObject(raw.data = e14a_data, min.cells = 3, min.genes = 200, 
                           project = "E14A")
e14a_meta = sample_sheet %>% filter(sample_id=="E14A")
e14a_meta_barcode = e14a_meta %>% select(cell_type)
rownames(e14a_meta_barcode) = substr(e14a_meta[,"sample_name"], 6, 19)
e14a = AddMetaData(object = e14a,
                   metadata = e14a_meta_barcode,
                   col.name = 'cell_type')
```

# Filter and normalize data, using default params
```{r}
e14a =  FilterCells(object = e14a, subset.names = "nGene", 
                        low.thresholds = 300, high.thresholds = 5000)
e14a = NormalizeData(object = e14a , 
                          normalization.method = "LogNormalize", 
                          scale.factor = 10000)
```
# Select purkinje cells
```{r}
e14a_purk = SubsetData(object = e14a, cells.use = e14a@meta.data$cell_type=="Purkinje")
```

Violin plots of purkinje markers in all cells versus authors annotated purkinje cells.
```{r}
VlnPlot(e14a, features.plot = c("Calb1", "Itpr1", "Mtss1", "Car8", "Gpr63", "Pcp2",
                                "Grid2", "Ebf1", "Rora"))
VlnPlot(e14a_purk, features.plot = c("Calb1", "Itpr1", "Mtss1", "Car8", "Gpr63", "Pcp2",
                                "Grid2", "Ebf1", "Rora"))
```

